Spatial and Temporal Analysis of Bicycle Thefts in Toronto

### 2024-11-08 paper/paper.Rmd
paper name changed, warnings and messages hided

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)

@@

```{r}
# Load the dataset
bike_thefts <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv"))

@@

```{r}
# Create a pie chart for the status of bicycle thefts
bike_thefts %>%
  count(STATUS) %>%
  ggplot(aes(x = "", y = n, fill = STATUS)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
  theme_minimal()
```

```{r}
# Create a bar chart for bicycle thefts by day of the week
bike_thefts %>%
  count(OCC_DOW) %>%
  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
  theme_minimal()
```

```{r}
# Load cleaned coordinates data
coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))

>>>>

```{r, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)

@@

```{r, include = TRUE, warning = FALSE, message = FALSE}
# Load the dataset
bike_thefts <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv"))

@@

```{r, include = TRUE, warning = FALSE, message = FALSE}
# Create a pie chart for the status of bicycle thefts
bike_thefts %>%
  count(STATUS) %>%
  ggplot(aes(x = "", y = n, fill = STATUS)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
  theme_minimal()
```

```{r, include = TRUE, warning = FALSE, message = FALSE}
# Create a bar chart for bicycle thefts by day of the week
bike_thefts %>%
  count(OCC_DOW) %>%
  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
  theme_minimal()
```

```{r, include = TRUE, warning = FALSE, message = FALSE}
# Load cleaned coordinates data
coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
